Appendix S1: Sampling patterns

### 2022-01-05 code/ms1_sampling.Rmd
updating just in case
started final revision

---
title: "sampling"
output: html_document
---

@@

## Visualize
```{r message=FALSE, warning=FALSE}
samplingplot1 <- ggplot(visitation_sampling, aes(x = year(date))) +
  geom_bar(fill = "gray60") +
  ylab("Total bumble bees\nobserved") +
  theme_light(13) +
  theme(axis.title.x = element_blank(),
        panel.grid.minor = element_blank(),
        panel.grid.major = element_blank())

samplingplot2 <- ggplot(bb_obs_per_sample, aes(x = year)) +
  geom_bar(fill = "gray60") +
  ylab("Total samples") +
  theme_light(13) +
  theme(axis.title.x = element_blank(),
        panel.grid.minor = element_blank(),
        panel.grid.major = element_blank())

samplingplot3 <- ggplot(bb_obs_per_sample, aes(x = year, y = obs)) +
  geom_violin(draw_quantiles = 0.5, fill = "gray60", color = NA) +
  geom_boxplot(fill = NA) +
  ylab("Bumble bees\nobserved / sample") +
  theme_light(13) +
  theme(axis.title.x = element_blank(),
        panel.grid.minor = element_blank(),
        panel.grid.major = element_blank())

samplingplot4 <- ggplot(bb_obs_per_sample, aes(as_date(yday(date)), elev.mean)) +
  geom_point(size = 1, aes(alpha = obs)) +
  facet_wrap(~year) +
  scale_alpha_continuous(name = "Bumble bees\nobserved") +
  scale_x_date(date_labels = "%b", breaks = as_date(c("1970-04-01", "1970-05-01", "1970-06-01",
                                                    "1970-07-01", "1970-08-01", "1970-09-01"))) +
  theme_light(13) +
  labs(x = NULL,
       y = "Elevation [m]") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1),
        panel.grid.minor = element_blank())

samplingplot <- ((samplingplot1 / samplingplot2 / samplingplot3) | samplingplot4) +
  plot_layout(widths = c(1, 3)) +
  plot_annotation(tag_levels = 'A')

ggsave("../ms_1/figures/fig2.pdf", samplingplot, height = 6, width = 10.5)
```

>>>>

---
title: "Appendix S1: Sampling patterns"
output: 
  pdf_document:
    # toc: true
    # toc_depth: 3
---

@@

## Visualize
```{r message=FALSE, warning=FALSE}
samplingplot1 <- ggplot(visitation_sampling, aes(x = year(date))) +
  geom_bar(fill = "gray60") +
  ylab("Total bumble bees\nobserved") +
  theme_light(10) +
  theme(axis.title.x = element_blank(),
        panel.grid.minor = element_blank(),
        panel.grid.major = element_blank())

samplingplot2 <- ggplot(bb_obs_per_sample, aes(x = year)) +
  geom_bar(fill = "gray60") +
  ylab("Total samples") +
  theme_light(10) +
  theme(axis.title.x = element_blank(),
        panel.grid.minor = element_blank(),
        panel.grid.major = element_blank())

samplingplot3 <- ggplot(bb_obs_per_sample, aes(x = year, y = obs)) +
  geom_violin(draw_quantiles = 0.5, fill = "gray60", color = NA) +
  geom_boxplot(fill = NA) +
  ylab("Bumble bees\nobserved / sample") +
  theme_light(10) +
  theme(axis.title.x = element_blank(),
        panel.grid.minor = element_blank(),
        panel.grid.major = element_blank())

samplingplot4 <- ggplot(bb_obs_per_sample, aes(as_date(yday(date)), elev.mean)) +
  geom_point(size = 1, aes(alpha = obs)) +
  facet_wrap(~year) +
  scale_alpha_continuous(name = "Bumble bees\nobserved") +
  scale_x_date(date_labels = "%b", breaks = as_date(c("1970-04-01", "1970-05-01", "1970-06-01",
                                                    "1970-07-01", "1970-08-01", "1970-09-01"))) +
  theme_light(10) +
  labs(x = NULL,
       y = "Elevation [m]") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1),
        panel.grid.minor = element_blank())

# samplingplot <- ((samplingplot1 / samplingplot2 / samplingplot3) | samplingplot4) +
#   plot_layout(widths = c(1, 3)) +
#   plot_annotation(tag_levels = 'A')

#ggsave("../ms_1/figures/fig2.pdf", samplingplot, height = 6, width = 10.5)

((samplingplot1 | samplingplot2 | samplingplot3) / samplingplot4)
```
